Intersection of non-matching grids of different dimensions

### 2016-09-22 paper_intersections.tex

\begin{figure}[!htb]
  \begin{center}        
    \def\svgwidth{0.7\textwidth}
    \input{\figpath plucker_products.pdf_tex}
%    \includegraphics{\figpath plucker_products.pdf}
  \end{center}
  \caption{Sign of the permuted inner product is related to the relative position of two oriented lines. Dashed line symbolizes that the line 
           is in the back, the llines intersect in the last case.}
  \label{fig:plucker_products}
\end{figure}

@@

\subsection{Tracking boundary of the intersection polygon}

\subsection{Prolongation algorithm}
Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
elements of the same dimension (1D, 2D), in the space of 3D elements (tetrahedrons). 
Obtaining of all the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.
Then we can prolongate the intersection by investigating neighbouring elements of the component.
%
\begin{figure}[!htb]
%   \vspace{0pt}
  \centering    
    \includegraphics[width=\textwidth]{\figpath prolongation_scheme.pdf}
  \caption{Prolongation algorithm for 1D-2D and 2D-3D intersections. }
  \label{fig:prolongation}
\end{figure}

The prolongation algorithm is the same for both 1D and 2D components, see \fig{fig:prolongation}. 
It can be seen as a \emph{breadth-first search}
\footnote{Wiki, [online 2016-03-01], \url{https://en.wikipedia.org/wiki/Breadth-first_search}}
algorithm on the graph of 1D and 2D elements, respectively.

@@

>>>>

\begin{figure}[!htb]
  \begin{center}        
    \includegraphics[width=0.7\textwidth]{\figpath plucker_product.pdf}
%    \includegraphics{\figpath plucker_products.pdf}
  \end{center}
  \caption{Sign of the permuted inner product is related to the relative position of two oriented lines. Dashed line symbolizes that the line 
           is in the back, the lines intersect in the last case.}
  \label{fig:plucker_products}
\end{figure}

@@

\subsection{Tracking boundary of the intersection polygon}
\notePE{I suggest to denote IP, IPs intersection point and its plural respectively.}

\notePE{It seems to me, that we can really describe the prolongation in general, for 1D and 2D, 
refering to them as components. I tried to do so..}

\notePE{We need proper definitions of terms we use: \\
\emph{component} is a set of connected elements of the same lower dimension (1D, 2D)\\
\emph{bulk} is a set of 3D elements\\
% or slave, master...
\emph{candidates pair}  is a pair of a component element and a bulk element, that might intersect
each other (due to intersection of their bounding boxes or prolongation result)
\emph{pathologic, special, degenerate case ??}
}

\notePE{Do you want to use American 'neighbor' or all other English 'neighbour'? (I prefer non-american.. to be unified at the end..)}

\subsection{Prolongation algorithm}
Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
elements of the same lower dimension (1D, 2D), in the space of 3D elements. 
Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.
Then we can prolongate the intersection by investigating neighbouring elements.
%
\begin{figure}[!htb]
%   \vspace{0pt}
  \centering    
    \includegraphics[width=\textwidth]{\figpath prolongation_scheme.pdf}
  \caption{Prolongation algorithm for 1D-2D and 2D-3D intersections. }
  \label{fig:prolongation}
\end{figure}

The prolongation algorithm is the same for both 1D and 2D components, see \fig{fig:prolongation}. 
It can be seen as a \emph{breadth-first search}
\footnote{Wiki, [online 2016-03-01], \url{https://en.wikipedia.org/wiki/Breadth-first_search}}
algorithm on the graph of component elements.

\textbf{breadth first search} algorithm:
  \begin{enumerate}
    \item\label{en:first} Get next unprocessed component element $k$.
    \item Find intersection candidates $\mathcal K$ in bulk mesh (3D elements).
    \item \label{en:q2}For $K\in \mathcal K$ compute intersection $(k, K)$.  
    \item Push the intersection neigbours into queues: $(k, L) \to Q_b$, $(l, K) \to Q_c$. 
    \item While $(l, L) \in Q_b$ check intersection $(l, L)$. Append queues.
    \item Pop pair from $Q_c$. (move to the next component element: go to \ref{en:q2}).
    \item If $Q_c$ is empty, go to \ref{en:first}.
  \end{enumerate}
  Prerequisites:
  \begin{itemize}
   \item need information about element connectivity (mesh preprocessing)
%   \item mark and check already inspected pairs. Marking elements + hashing.
   \item find the starting intersection -- AABB (Axes Aligned Bounding Boxes) 
   \item possibly create Bounding Interval Hierarchy (BIH)
%   \item Pass already known information with pairs.
%   \item Deal with degenerated cases.
  \end{itemize}

@@

% \subsubsection{1D-3D prolongation}
% 1d-3d prolongation logic
% IP is:
% - 1D element node
%     - inside tetrahedron
%         - get the neighboring 1D element
%         - push to component queue candidate pair [1D neigbor -- tetrahedron]
%     - on the surface of tetrahedron
%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
%         - get the tetrahedron neighbors on the faces
%         - push to bulk queue new candidates pairs:
%             - [current 1D element -- tetrahedron neighbor]
%             - [1D neighbor -- tetragedron neighbor]
%             - check whether the candidate pair has not been computed yet
%             (- if no new prolongation, push empty pair; means IP is on the boundary; 
%                the element is not closed then -- not fully covered with tetrahedrons)
% - inside 1D element
%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
%     - get the tetrahedron neighbors on the faces
%     - push to bulk queue candidate pair [current 1D element -- tetrahedron neighbor]
%     - check whether the candidate pair has not been computed yet
%     (- if no new prolongation, push empty pair; same meaning as above)

% A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases:

% \begin{itemize}
%     \item \textbf{IP lies at 1D element node and inside 3D element} \\
%             We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
%     \item \textbf{IP lies at 1D element node and on the surface of 3D element} \\
%             We find all the faces of 3D element in which the IP lies (1 face, or 2 faces (IP on an edge), 
%             or 3 faces (IP at a node)). We find the corresponding neghboring 3D elements over the faces and
%             push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
%             If the candidates pair has been investigated already, we skip it.
%     \item \textbf{IP lies inside 1D element (therefore must be on the surface of 3D element)} \\
%             The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
%             there is no 1D neighbor.
% \end{itemize}

A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases (applies both for 1D-3D and 2D-3D):
\begin{itemize}
    \item \textbf{IP lies on component element side and inside bulk element} \\
            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
            We find the component neighboring elements over the sides and push a new candidate pair
            [component neighbor -- current bulk element] into component queue.
    \item \textbf{IP lies on component element side and on the surface of bulk element} \\
            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
            push the following new candidates pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
            If the candidates pair has been investigated already, we skip it.
    \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
            The same as before, but we push only [current component element -- bulk neighbor] candidates pairs, since
            there is no component neighbor.
\end{itemize}

% 2d-3d prolongation logic CURRENT
% IP is:
% - inside 2D element side
%     - inside 3D element
%         - get the neighboring 2D elements over the side
%         - push to component queue candidates pair [2D neigbor -- current 3D element]
% - inside the face of 3D element
%     - get the neighboring 3D element over the face
%     - push to bulk queue candidate pair [2D neighbor -- 3D element]
% 
% 2d-3d prolongation logic WITH FUTURE CORRECTIONS
% IP is:
% - on 2D element side
%     - find 2D element sides (if at node) and the corresponding neighbors
%     - inside 3D element
%         - push to component queue candidates pairs [2D neigbor -- current 3D element]
%     - on the surface of 3D element
%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
%         - get the 3D neighbors over the faces
%         - push to bulk queue new candidates pairs
%             - [current 2D element -- 3D neighbor]
%             - [2D neighbor -- 3D neighbor] (all combinations)
%             - check whether the candidate pair has not been computed yet
% - inside the 2D element (=> on the surface of 3D element)
%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
%     - get the 3D neighbors over the faces
%     - push to bulk queue new candidates pairs [current 2D element -- 3D neighbor]
%     - check whether the candidate pair has not been computed yet
